### 2014-07-23 Quality_Reports/Strand_exploration.Rmd
added figure 5 from carrol et al 2014 to document

@@

>>>>

A graphical explanation of this effect is given in the figure 5 of [Carroll et. al. 2014's paper](http://journal.frontiersin.org/Journal/10.3389/fgene.2014.00075/full):

![plot of fraglen est. by cross - corr.](figure/fromPaper/figure5-carroll-2014.jpg)

In this figure we can see:

@@

```{r init,include = FALSE,echo = TRUE,results = "hide"}
library(GenomicAlignments)
library(parallel)
library(knitr)
dr ="/NO_BACKUP/KelesGroup_DongjunChung/ChIP-exo/Landick_ChIP-exo3/rawdata"
folder = c("ChIPexo","ChIPseq_PET","ChIPseq_SET")
files = lapply(folder,function(x,dr){
  ff = list.files(file.path(dr,x))
  return(ff[!grepl("bai",ff) & !grepl("sam",ff)])},dr)
names(files) = folder
ff = lapply(folder,function(x,dr,files)file.path(dr,x,files[[x]]),dr,files)
names(ff) = folder
design = data.frame(Rep = c(rep(1,4),rep(2,4)),Rif = rep(c(0,0,20,20),2),IP = rep(c("Sigma70","BetaPrimeFlag"),4),
  exo.edns = c(1311,1312,1314,1315,1317,1318,1320,1321),pet.edsn = seq(1396,1403))
betaF = data.frame(Rep = c(1,1,2,2),Rif = c(0,20,0,20),IP = rep("Beta",4),exo.edns = c(1310,1313,1316,1319))
start = c(576875,798921,1152674,1192831,1820005,2310506,2996662,3351853,3973436,4262028)
end = c(577492,799434,1153291,1193448,1820696,2311153,2997175,3352366,3973949,4262541)
peaks = GRanges(seqnames = "U00096",ranges = IRanges(start = start,end = end),strand = "*")
width(peaks) = 1000
```

```{r show_df,include = TRUE,echo = FALSE,results = "asis"}
kable(design,format = "markdown")
```
